%Text Books : \cite{fraleigh}
%Module 1
%Direct products and finitely generated Abelian groups, fundamental theorem, Applications
%Factor groups, Fundamental homomorphism theorem, normal subgroups and inner automorphisms.
%Group action on a set, Isotropy subgroups, Applications of G- sets to counting.
%(Part II – Sections 11, 14, 16 & 17) (25 hours)
%Module 2
%Isomorphism theorems, Sylow theorems , Applications of the Sylow theory.
%(Part VII Sections34, 36 & 37) (25 hours)
%Module 3
%Fermat’s and Euler Theorems, The field of quotients of an integral domain,
%Rings of polynomials, Factorisation of polynomials over a field.
%(Part IV – Sections 20, 21, 22 & 23) (20 hours)
%Module 4
%Non commutative examples, Homeomorphisms and factor rings, Prime and
%Maximal Ideals
%(Part V – Sections 24, 26 & 27) (20 hours)

\chapter{ME010101 Abstract Algebra}
\textit{Text book : John B. Fraleigh, A first course in abstract algebra, 7th edition, Pearson Education, 2003}
\begin{enumerate}[label=Topic \arabic*]
	\item Fundamental Theorem for Abelian Groups
	\begin{enumerate}[label=Session \arabic*]
		\item Introduction to Abstract Algebra.
		\item Direct product of Groups.
		\item Finitely generated Abelian Groups.
	\end{enumerate}
	\item Fundamental Homomorphism Theorem for Groups
	\begin{enumerate}[label=Session \arabic*]
		\item Cosets and Homomorphism.
		\item Factor Groups.
		\item Fundamental Homomorphism \& Automorphism.
		\item Simple Groups.
	\end{enumerate}
	\item Group Action
	\begin{enumerate}[label=Session \arabic*]
		\item Group Action.
		\item Isotropy Subgroups.
		\item Burnside's forumula.
	\end{enumerate}
	\item Nonabelian Groups : Isomorphism Theorems
	\begin{enumerate}[label=Session \arabic*]
		\item First Isomorphism Theorem.
		\item Second Isomorphism Theorem.
		\item Third Isomorphism Theorem.
	\end{enumerate}
	\item Nonabelian Groups : Sylow Theorems
	\begin{enumerate}[label=Session \arabic*]
		\item Cauchy's Theorem.
		\item First Sylow's Theorem.
		\item Second Sylow's Theorem.
		\item Third Sylow's Theorem.
	\end{enumerate}
	\item Applications of Sylow Theorems
	\begin{enumerate}[label=Session \arabic*]
		\item Applications.
		\item More Applications.
	\end{enumerate}
	\item Field of Quotients of an Integral Domain
	\begin{enumerate}[label=Session \arabic*]
		\item Rings, Fields \& Integral Domains.
		\item Fermat, Euler Theorems.
		\item Field of Quotients.
	\end{enumerate}
	\item Rings
	\begin{enumerate}[label=Session \arabic*]
		\item Ring of Polynomials.
		\item Evaluation Homomorpism.
		\item Factor Theorem.
		\item Irreducible Polynomials.
		\item Unique factorisation.
	\end{enumerate}
	\item Endomorphisms and Group Rings
	\begin{enumerate}[label=Session \arabic*]
		\item Group Rings.
		\item Finite Division Ring.
	\end{enumerate}
	\item Fundamental Homomorphism Theorem for Rings
	\begin{enumerate}[label=Session \arabic*]
		\item Homomorphism.
		\item Factor Ring.
		\item Fundamental Homomorphism Theorem.
	\end{enumerate}
	\item Ideals
	\begin{enumerate}[label=Session \arabic*]
		\item Ideals.
		\item Maximal, Prime Ideals.
		\item Prime Fields.
	\end{enumerate}
\end{enumerate}
