%Text Books : \cite{apostol}, \cite{rudin}

%Module 1:
%The Weirstrass theorem, other forms of Fourier series, the Fourier integral theorem, the exponential form of the Fourier integral theorem, integral transforms and convolutions, the convolution theorem for Fourier transforms.
%(Chapter 11 Sections 11.15 to 11.21 of \cite{apostol}) (20 hours.)
%Module 2:
%Multivariable Differential Calculus, The directional derivative, directional derivatives and continuity, the total derivative, the total derivative expressed in terms of partial derivatives, An application of complex- valued functions, the matrix of a linear function, the Jacobian matrix, the matrix form of the chain rule. Implicit functions and extremum problems, the mean value theorem for differentiable functions,
%(Chapter 12 Sections. 12.1 to 12.11 of \cite{apostol}) (22 hours.)
%Module 3: 
%A sufficient condition for differentiability, a sufficient condition for equality of mixed partial derivatives, functions with non-zero Jacobian determinant, the inverse function theorem ,the implicit function theorem, extrema of real- valued functions of one variable, extrema of real-valued functions of several variables.
%Chapter 12 Sections-. 12.12 to 12.13 of \cite{apostol} 
%Chapter 13 Sections-. 13.1 to 13.6 of \cite{apostol} (28 hours.)
%Module 4:
%Integration of Differential Forms- Integration, primitive mappings, partitions of unity, change of variables, differential forms.
%(Chapter 10 Sections. 10.1 to 10.14 of \cite{rudin}) (20 hours)

\chapter[multivariate calculus]{ME010303 Multivariate Calculus \& Integral Transforms}
\textit{Textbooks : Tom M. Apostol, Mathematical Analysis, 2nd Edition, Addison-Wesley, 1974\\Walter Rudin, Principles of mathematical analysis, 3rd Edition}
\begin{enumerate}[label=Week \arabic*]
	\item Weierstrass approximation theorem, other forms of Fourier series, Fourier integral theorem, exponential form of Fourier integral theorem, integral transforms. Reading : \S 11.15-20
	\item Directional derivatives, Total Derivative, Complex valued functions, matrix of linear functions, Jacobian matrix. Reading: \S 12.1-8
	\item chain rule, matrix form of chain rule, mean-value theorem. Reading : \S 12.9-11\footnote{Semester 2, University Examinations}
	\item Reading : \S12.12-13
		\begin{enumerate}[label=Day \arabic*]
			\item Sufficient condition for differentiability. Reading : \S12.12
			\item Sufficient condition for equality of partial derivatives. Reading : \S12.13
		\end{enumerate}
		\textbf{Jan 08, 2020} Internal Examination Module 2
	\item  Reading : \S13.1-4
		\begin{enumerate}[label=Day \arabic*]
			\item Implicit function, Jacobian determinant $J_f(\overline{x})$, Jacobian determinant of complex-valued functions \S13.1
			\item Continuity of $f$ with $J_f(\overline{x}) \ne 0$. Reading : \S13.2 Theorem 13.2
			\item Function $f$ with $J_f(\overline{x}) \ne 0$ is an open mapping. \S13.2 Theorem 13.3
			\item Inverse function therorem. Reading : \S13.3
			\item Implicit function theorem. Reading : \S13.4
		\end{enumerate}
		\textbf{Jan 15, 2020}
	\item  Reading : \S 13:5-6
		\begin{enumerate}[label=Day \arabic*]
			\item Extrema of function on one variable. Reading : \S13.5
			\item Extrema of functions on several variables. Reading : \S13.6
		\end{enumerate}
		\textbf{Jan 22, 2020}
	\item Convolution theorem for Fourier transforms. Reading : \S 11.21 (pending)\\
		\textbf{Jan 29, 2020}
	\item  Reading : \S10.1-9
		\begin{enumerate}[label=Day \arabic*]
			\item k-cell $I_k$, integration over k-cell, support, primitive mappings, flip, local represenation as composition of primitives and flips, partitions of unity, change of variables on continuous functions with compact support. 
		\end{enumerate}
		\textbf{Feb 05, 2020}
	\item  Reading : \S10.10-14
		\begin{enumerate}[label=Day \arabic*]
			\item k-surface, k-form (differential form of order $k$), properties of $k$-forms, basic $k$-forms.
		\end{enumerate}
		\textbf{Feb 12, 2020}
\end{enumerate}
