%Text Books: \cite{thorpe}
%Module 1:
%Graphs and level sets, vector fields, the tangent space, surfaces, vector fields on surfaces, orientation.
%(Chapters 1 to 5 of \cite{thorpe}) (20 hours)
%Module 2:
%The Gauss map, geodesics, Parallel transport,
%(Chapters 6, 7 & 8 of \cite{thorpe}) (20 hours)
%Module 3:
%The Weingarten map, curvature of plane curves, Arc length and line integrals
%(Chapters 9, 10 & 11 of \cite{thorpe}) (25 hours)
%Module 4:
%Curvature of surfaces and Parametrized surfaces
%(Chapters 12 & 14 of \cite{thorpe}) (25 hours)

\chapter{ME800401 Differential Geometry}
\textit{Text book : J. A. Thorpe, Elementary topics in Differential Geometry, Springer, 1979}
\begin{enumerate}[label=Week \arabic*]
	\item Reading : \S1, \S2, \S3
	\begin{enumerate}[label=Day \arabic*]
		\item Graphs and Level Sets. Reading : \S1
		\item Vector Fields. Reading : \S2
		\item Maximal Integral Curve. Reading : \S2
		\item Tangent Space. Reading : \S3
		\item 
	\end{enumerate}
	\item Reading : \S4, \S5
	\begin{enumerate}[label=Day \arabic*]
		\item Surface. Reading : \S4
		\item Vector Fields on Surfaces. Reading : \S5
		\item Maximal Integral Curve. Reading : \S5
		\item Orientation. Reading : \S5
		\item
	\end{enumerate}
	\item Reading : \S6, \S7
	\begin{enumerate}[label=Day \arabic*]
		\item Gauss Map. Reading : \S6
		\item Gauss map is onto. Reading : \S6
		\item Geodesics. Reading : \S7
		\item Maximal Geodesic. Reading : \S7
		\item
	\end{enumerate}
	\item Reading : \S8
	\begin{enumerate}[label=Day \arabic*]
		\item Covariant Differentiation. Reading : \S8
		\item Levi-Civita Parallel. Reading : \S8
		\item Parallel Transport. Reading : \S8
		\item Properties of Parallel Transport. Reading : \S8
		\item
	\end{enumerate}
	\item Reading : \S9,\S10
	\begin{enumerate}[label=Day \arabic*]
		\item Directional Derivatives. Reading : \S9
		\item Weingarten map. Reading : \S9
		\item Properties of Weingarten Map. Reading : \S9
		\item Curvature of Plan Curves. Reading : \S10
		\item
	\end{enumerate}
	\item Reading : \S11
	\begin{enumerate}[label=Day \arabic*]
		\item Length of parameterised Curve. Reading : \S11
		\item Existence of global parameterisation. Reading : \S11
		\item Unit speed global parameterisation. Reading : \S11
		\item Differential Forms. Reading : \S11
		\item
	\end{enumerate}
	\item Reading : \S12
	\begin{enumerate}[label=Day \arabic*]
		\item Normal Curvature of Surfaces. Reading : \S12
		\item 
		\item
		\item 
		\item
	\end{enumerate}
	\item Reading : \S14
	\begin{enumerate}[label=Day \arabic*]
		\item 
		\item 
		\item
		\item 
		\item
	\end{enumerate}
\end{enumerate}
